% Created 2023-01-02 Mon 22:32
% Intended LaTeX compiler: pdflatex
\documentclass[article, 11pt]{article}
                      \usepackage{lmodern} % Ensures we have the right font
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsmath, amsthm, amssymb}
\usepackage[table, xcdraw]{xcolor}
\usepackage{listings}
\definecolor{bblue}{HTML}{0645AD}
\usepackage[colorlinks]{hyperref}
\hypersetup{colorlinks, linkcolor=blue, urlcolor=bblue}
\usepackage{titling}
\setlength{\droptitle}{-6em}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1em}
\usepackage[stretch=10]{microtype}
\usepackage{hyphenat}
\usepackage{ragged2e}
\usepackage{subfig} % Subfigures (not needed in Org I think)
\usepackage{hyperref} % Links
\usepackage{listings} % Code highlighting
\usepackage[top=1in, bottom=1.25in, left=1.55in, right=1.55in]{geometry}
\renewcommand{\baselinestretch}{1.15}
\usepackage[explicit]{titlesec}
\pretitle{\begin{center}\fontsize{20pt}{20pt}\selectfont}
\posttitle{\par\end{center}}
\preauthor{\begin{center}\vspace{-6bp}\fontsize{14pt}{14pt}\selectfont}
\postauthor{\par\end{center}\vspace{-25bp}}
\predate{\begin{center}\fontsize{12pt}{12pt}\selectfont}
\postdate{\par\end{center}\vspace{0em}}
\titlespacing\section{0pt}{5pt}{5pt} % left margin, space before section header, space after section header
\titlespacing\subsection{0pt}{5pt}{-2pt} % left margin, space before subsection header, space after subsection header
\titlespacing\subsubsection{0pt}{5pt}{-2pt} % left margin, space before subsection header, space after subsection header
\usepackage{enumitem}
\setlist{itemsep=-2pt} % or \setlist{noitemsep} to leave space around whole list
\titleformat{\section} {\Large}{\thesection}{1em}{\textbf{#1}} % Section header formatting
\titlespacing\section{0pt}{5pt}{-5pt} % left margin, space before section header, space after section header
\titleformat{\subsection} {\large}{\thesubsection}{1em}{\textbf{#1}}
\titlespacing\subsection{0pt}{5pt}{-5pt} % left margin, space before subsection header, space after subsection header
\titleformat{\subsubsection} {\large}{\thesubsubsection}{1em}{#1}
\titlespacing\subsubsection{0pt}{5pt}{-5pt} % left margin, space before subsection header, space after subsection header
\author{Keith Butler}
\date{2022-09-26 Mon}
\title{Game Design Document\\\medskip
\large More words}
\begin{document}


\newcommand{\gameName}{Fancy Name}
\newcommand{\shortDescription}{Short description of the game}

\begin{titlepage}
\begin{center}
\title {
    Game Design Document
    \\
    \vspace{7cm}
    {\huge \gameName}
}

\maketitle
\nopar\noindent\rule{\textwidth}{0.4pt}
\begin{center}\shortDescription\end{center}
\nopar\noindent\rule{\textwidth}{0.4pt}
\vspace{15mm}

\end{center}
\end{titlepage}

\tableofcontents

\section{Game Overview}
\label{sec:org28b3e93}
\subsection{Concept}
\label{sec:orgf00c6ca}

Introduction of the concept.
\subsection{Feature Set}
\label{sec:org8b4b075}
\subsection{Genres}
\label{sec:org5731449}
Top down twin stick shooter
\subsection{Target Audience}
\label{sec:orgc224b84}

Main target audiences of the game and reasoning why game attracts certain audiences.
\subsection{Game Flow Summary - How does the player move through the game? Both through framing interface and the game itself.}
\label{sec:orgeb3b559}
\subsection{Look and Feel - What is the basic look and feel of the game? What is the visual style? Give examples}
\label{sec:org5c2b2d1}
Briefly explaining how the game looks and feels.
\subsection{Project Scope - A Summary of the scope of the game.}
\label{sec:org7bbcfe3}
\subsubsection{Number of locations}
\label{sec:orgce2caf4}
\subsubsection{Number of levels}
\label{sec:org60de23d}
\subsubsection{Number of NPC's}
\label{sec:orgc00d0c8}
\subsubsection{Number of  weapons}
\label{sec:org12090dc}
\subsubsection{Etc.}
\label{sec:orgcc0498b}
\subsection{Unique Selling Point}
\label{sec:orge9d0199}
What makes this game stand out?

\section{Gameplay and mechanics}
\label{sec:org41212f7}
\subsection{Gameplay}
\label{sec:org7a82921}
\subsubsection{Game Progression}
\label{sec:orgc3f6270}
\subsubsection{Mission/Challenge Structure}
\label{sec:org840efdc}
\subsubsection{Puzzle Structure}
\label{sec:org8d815d2}
\subsubsection{Objectives - What are the objectives of the game?}
\label{sec:org7425bf5}
\subsubsection{Play Flow - How does the game flow for the game player}
\label{sec:orgbdeb225}
\subsection{Mechanics - What are the rules to the game, both implicit nad explicit? This is the model of the unvierse that the game works under. Think of it as a simulation of the world, how do all the pieces interact? This actually can be a very large section}
\label{sec:org7241c87}
\subsubsection{Physics - How does the physical universe work?}
\label{sec:orgee72f77}
\subsubsection{Movement}
\label{sec:org322f010}
\begin{enumerate}
\item General Movement
\label{sec:org55d12da}
\item Other Movement
\label{sec:org887facf}
\end{enumerate}
\subsubsection{Objects}
\label{sec:org6a487d3}
\begin{enumerate}
\item Picking Up Objects
\label{sec:orgd381bee}
\item Moving Objects
\label{sec:org730cd22}
\end{enumerate}
\subsubsection{Actions}
\label{sec:org8464467}
\begin{enumerate}
\item Switches and Buttons
\label{sec:org8f03a80}
\item Picking up, Carrying and Dropping
\label{sec:orgf217cd4}
\item Talking
\label{sec:orge7db481}
\item Reading
\label{sec:org5cebd86}
\end{enumerate}
\subsubsection{Combat - If there is combat or even conflict, how is this specifically modelled?}
\label{sec:orgec8a7cf}
\subsubsection{Economy - What is the exonomy of the game? How does it work?}
\label{sec:org144a7b0}
\subsection{Screen Flow}
\label{sec:org76e3a4c}
\subsubsection{Screen Flow Chart - A Graphical description of How each screen is related to each other}
\label{sec:orga5271fc}
\subsubsection{Screen Descriptions - What is the purpose of each screen?}
\label{sec:orgcb7af26}
\begin{enumerate}
\item Main Menu Screen
\label{sec:orgbb2c741}
\item Options Screen
\label{sec:orgb0c6004}
\item Etc.
\label{sec:org7bf9e07}
\end{enumerate}
\subsubsection{Game Options - What are the options and how do they affect gameplay and mechanics?}
\label{sec:orgaa0109a}
\subsubsection{Replaying and saving}
\label{sec:org9cce058}

\section{Story, Setting and Character}
\label{sec:orgd94209c}
\subsection{Story and Narrative}
\label{sec:org0c361a4}
\subsubsection{Back Story}
\label{sec:org99d40cd}
\subsubsection{Plot Elements}
\label{sec:org5b3d337}
\subsubsection{Game Progression}
\label{sec:org8243dd7}
\subsubsection{Cut Scenes}
\label{sec:org636bd67}
\begin{enumerate}
\item Cut scene 1
\label{sec:org3040d4d}
\begin{enumerate}
\item Actors
\label{sec:orgd47ce13}
\item Description
\label{sec:org7693de3}
\item Storyboard
\label{sec:org8e16ec0}
\item Script
\label{sec:org873ee96}
\end{enumerate}
\item Cut scene 2
\label{sec:org9d07106}
\item Etc.
\label{sec:org7361acd}
\end{enumerate}
\subsection{Game World}
\label{sec:orgce45647}
\subsubsection{Genral look and feel of the world}
\label{sec:orgc93a775}
\subsubsection{Area 1}
\label{sec:orgaadeebf}
\begin{enumerate}
\item General Description
\label{sec:org796ec0f}
\item Phyical Characteristics
\label{sec:orgfd9fab3}
\item Levels that use area
\label{sec:orgf0eb880}
\item Connections to other areas
\label{sec:orgfa9067e}
\end{enumerate}
\subsubsection{Area 2}
\label{sec:orga88d4fe}
\begin{enumerate}
\item Etc.
\label{sec:orga12cd86}
\end{enumerate}
\subsection{Characters}
\label{sec:orgb10fc3b}
\subsubsection{Character 1}
\label{sec:org0ee6148}
\begin{enumerate}
\item Back Story
\label{sec:org3cd49f9}
\item Personality
\label{sec:org51c817e}
\item Look
\label{sec:org769ff2a}
\begin{enumerate}
\item Physical Characteristics
\label{sec:orgbb0ade0}
\item Animations
\label{sec:org1cb9045}
\end{enumerate}
\item Special Abilities
\label{sec:orgcf01417}
\item Relevance to game story
\label{sec:org7047a71}
\item Relationship to other characters
\label{sec:org4a9f279}
\item Statistics
\label{sec:org8d5a074}
\end{enumerate}
\subsubsection{Character 2}
\label{sec:orge874286}

\section{Levels}
\label{sec:org20204b1}
\subsection{Level 1}
\label{sec:org26baa69}
\subsubsection{Synopsis}
\label{sec:orgd9b5ac3}
\subsubsection{Introductory Material ( Cut scene? Mission briefing? )}
\label{sec:orgeb91eac}
\subsubsection{Objectives}
\label{sec:org1e7e4a0}
\subsubsection{Physical Description}
\label{sec:org7ec03e9}
\subsubsection{Map}
\label{sec:orga5f802e}
\subsubsection{Critial Path}
\label{sec:org1eb95f1}
\subsubsection{Encounters}
\label{sec:org94f24ef}
\subsubsection{Level Walkthrough}
\label{sec:org1bfed02}
\subsubsection{Closing Material}
\label{sec:org9ab08a9}
\subsection{Level 2}
\label{sec:orgd1fcf5e}
\subsection{Etc.}
\label{sec:orgb94df7a}
\subsection{Training Level}
\label{sec:org8045101}

\section{Interface}
\label{sec:org4723053}
\subsection{Visual System}
\label{sec:org64cfdb4}
\subsubsection{HUD - What controls}
\label{sec:org4060648}
\subsubsection{Menus}
\label{sec:org0fc22ea}
\subsubsection{Rendering System}
\label{sec:orga9f72cd}
\subsubsection{Camera}
\label{sec:orgdd8c7b1}
\subsubsection{Lighting Models}
\label{sec:orgc630454}
\subsection{Control System - How does the game player control the game? What are the specific commands?}
\label{sec:org1316122}
\subsection{Audio}
\label{sec:org011bcf2}
\subsection{Music}
\label{sec:org32dd5d3}
\subsection{Sound Effects}
\label{sec:orgd37d7da}
\subsection{Help System}
\label{sec:org43da82c}

\section{Artificial Intelligence}
\label{sec:orgf27ac17}
\subsection{Opponent AI - The active opponent that plays against the game player and therefore requires strategic decisions making (example, Civilization or Chess, how is it to be disigned?)}
\label{sec:org6119ea5}
\subsection{Enemy AI - Villains and Monsters}
\label{sec:org68ecf18}
\subsection{Non-combat Characters}
\label{sec:org07bfdb8}
\subsection{Friendly characters}
\label{sec:org1198f8f}
\subsection{Support AI}
\label{sec:orga58f6f6}
\subsubsection{Player and Collision detection}
\label{sec:orgc7eb419}
\subsubsection{Pathfinding}
\label{sec:org39213e9}

\section{Technical}
\label{sec:org42b8122}
\subsection{Target Hardware}
\label{sec:org831965e}
\subsection{Development hardware and software}
\label{sec:org8e3cdd3}
\subsection{Development procedures and standards}
\label{sec:org582b00a}
\subsection{Game Engine}
\label{sec:org28adf12}
\subsection{Network}
\label{sec:orgb8fb21f}
\subsection{Scripting Language}
\label{sec:org0220519}
\subsection{Etc.}
\label{sec:orgb16d09d}

\section{Game Art}
\label{sec:org32cb3d3}
\subsection{Concept Art}
\label{sec:org7491a6f}
\subsection{Style Guides}
\label{sec:orgf31bfb1}
\subsection{Characters}
\label{sec:orgf531b6f}
\subsection{Enviroment}
\label{sec:org7736a76}
\subsection{Equipment}
\label{sec:org7fe7247}
\subsection{Cut Scenes}
\label{sec:org1399539}
\subsection{Miscellaneous}
\label{sec:org1410570}

\section{Project Management}
\label{sec:org05f1edb}
\subsection{Project Methodology: Pick one, justify it, hsow how you plan to tailor it to your project. Do not write in generic terms}
\label{sec:org6902fc6}
\subsection{Detailed Schedule: Including major project milestones and sprint deadlines if using an agile-type methodology}
\label{sec:org0dfc38d}
\subsection{Schedule Management: Select a tool (such as JIRA, trello, etc.) and justify your selection}
\label{sec:orged29479}
\subsection{Version control, Select a tool (such as Git/Github, Unity Collaborate. etc.) and justify your selection}
\label{sec:org5d37b34}
\subsection{Risk Analysis}
\label{sec:org769fb0e}
\subsection{Test Plan: How will you test your game? How will you playtest your game?}
\label{sec:org07f38ee}

\section{Appendices}
\label{sec:org18fa6c6}
\begin{itemize}
\item \href{https://github.com/viirret/gdd-template/blob/main/main.tex}{gdd-template/main.tex at main · viirret/gdd-template · GitHub}
\end{itemize}
\subsection{Credits: List ALL third-party assets used in your game. Group them according to type:}
\label{sec:org928bbc0}
\subsubsection{Images}
\label{sec:orgad24e9c}
\subsubsection{Models}
\label{sec:org634a8f3}
\subsubsection{Animations}
\label{sec:org5b017ba}
\subsubsection{Audio}
\label{sec:org1f7bed0}
\subsubsection{Cameras}
\label{sec:orgc7fbb61}
\subsubsection{Player controllers}
\label{sec:org0cbd4ce}
\subsubsection{Etc.}
\label{sec:org047b000}
\subsection{References. Use the Harvard method to format references for all in-text citations}
\label{sec:orga146072}
\subsection{Project logs. Weekly/fortnightly log, such as Sprint doc ( if using Scrum ), Trello charts, Youtube vlog, etc.}
\label{sec:org5a980dd}
\end{document}